Analysis2

### 2023-10-26 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
Added index variable for decade born for replication

>>>>

```{r}
#Create a column which described the decade a player was born in

Batting %>% 
  #Put the birth year down to the decade value. (i.e. 1936 becomes 193.6)
  #Then force it to be an integer. R doesn't round so we are left with (1936=193) a decade
  mutate(birthDecade = as.integer(birthYear/10), .before=birthYear) %>% 
  #Then, index it by making the minimum year equal to 1
  mutate(birthDecade = birthDecade - min(birthDecade) + 1)
```
